---
output: github_document
---

```{r echo=FALSE, results = 'asis'}
pkg <- 'qap'

source("https://raw.githubusercontent.com/mhahsler/pkg_helpers/main/pkg_helpers.R")
pkg_title(pkg)
```

This package implements heuristics for the Quadratic Assignment Problem (QAP) 
first introduced by Koopmans and Beckmann (1957).
Although, the QAP was introduced as a combinatorial optimization problem for the facility location problem in operations research, it also has many applications in data analysis (see Hubert and Schultz; 1976).

The problem is NP-hard and the package implements the simulated annealing heuristic described in [Burkard and Rendl (1984)](#BR1984).

```{r echo=FALSE, results = 'asis'}
pkg_install(pkg)
```

## Usage

Load the had12 QAPLIB problem (shipped with the package). The problem contains the A and B matrices and the optimal solution. We run 10 repetitions and use the best solution.
```{r}
library(qap)
set.seed(1000)

p <- read_qaplib(system.file("qaplib", "had20.dat", package="qap"))
p$opt

a <- qap(p$A, p$B, rep = 10)
a
```

Compare with known optimum (% above optimum).
```{r}
(attr(a, "obj") - p$opt)/p$opt * 100
```

## References

* 
```{r results="asis", echo = FALSE} 
  print(citation("qap"), style = "text")
```
* <a id = "BR1983" />R.E. Burkard and F. Rendl (1984). A thermodynamically motivated simulation procedure for combinatorial optimization problems. _European Journal of Operations Research,_ 17(2):169-174.
  https://doi.org/10.1016/0377-2217(84)90231-5
* Koopmans TC, Beckmann M (1957). Assignment problems and the location of economic activities. _Econometrica_ 25(1):53-76.
  https://doi.org/10.2307/1907742
* Hubert, L., and Schultz, J. (1976). Quadratic assignment as a general data analysis strategy. 
  _British Journal of Mathematical and Statistical Psychology,_ 29(2), 190–241. 
  https://doi.org/10.1111/j.2044-8317.1976.tb00714.x


