---
output: github_document
---

```{r echo=FALSE, results = 'asis'}
pkg <- 'qap'

source("https://raw.githubusercontent.com/mhahsler/pkg_helpers/main/pkg_helpers.R")
pkg_title(pkg)
```

Implements heuristics for the Quadratic Assignment Problem (QAP). Currently only the simulated annealing heuristic described in Burkard and Rendl (1984) is available. 

```{r echo=FALSE, results = 'asis'}
pkg_install(pkg)
```

## Usage

Load the had12 QAPLIB problem (shipped with the package). The problem contains the A and B matrices and the optimal solution. We run 10 repetitions and use the best solution.
```{r}
library(qap)
set.seed(1000)

p <- read_qaplib(system.file("qaplib", "had20.dat", package="qap"))
p$opt

a <- qap(p$A, p$B, rep = 10)
a
```

Compare with known optimum (% above optimum).
```{r}
(attr(a, "obj") - p$opt)/p$opt * 100
```

## References

* R.E. Burkard and F. Rendl. A thermodynamically motivated simulation procedure for combinatorial optimization problems. _European Journal of Operations Research,_ 17(2):169-174, 1984.
* [qap package reference manual.](https://cran.r-project.org/package=qap/qap.pdf)

